Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-22 paper/icml_drau/discussions.tex

\paragraph{Smoothness of the value function.} In all of our proofs, $V^\pi$ is
assumed to be continuously differentiable for all $\pi$.  This %is a strong
hypothesis is not always satisfied in practice. Very simple environments
break this hypothesis, such as the pendulum swing-up environment,
with pendulum height as reward and torque as action.  Indeed, 
% assume that $\pi$
% is the optimal policy for the pendulum swing-up environment, with state
% representation $(\theta, \dot{\theta})$. 
the state space $(\theta, \dot{\theta})$ for this environment
can be partitioned into two subspaces $\mathcal{G}$ and $\mathcal{B}$, with
$\mathcal{G}$ the subspace where the optimal policy 
can swing up the pendulum without crossing the $y$-axis, and $\mathcal{B}$ where
it has to cross the $y$-axis. The difference of $V$-function between a point in
$\mathcal{G}$ and a point in $\mathcal{B}$ is lower bounded by a finite
quantity. 
%Besides, one can find two points $s_1 \in \mathcal{G}$ and $s_2 \in \mathcal{B}$
%such that $s_1$ and $s_2$ are arbitrarily close.
Consequently, the value function is
discontinuous on the frontier between $\mathcal{G}$ and $\mathcal{B}$, which results in non infinitesimal advantages
for actions taken on the frontier. \TODO{Non infinitesimal advantages are found,
more generally, as soon as a given policy has different regimes depending on
where it starts in state space. For such policies the value
function is typically discontinuous at the frontier between two
regimes, resulting in non infinitesimal advantages. The
continuous-time DAU properties would only hold almost-everywhere.}

>>>>

\paragraph{Smoothness of the value function.} In all of our proofs, $V^\pi$ is
assumed to be continuously differentiable for all $\pi$.  This %is a strong
hypothesis is not always satisfied in practice. 
\TODO{For instance, in the pendulum swing-up environment, depending on initial
position and momentum, the optimal policy may need to turn round a
certain number of times before reaching the desired state. At the
points of state space where the number of turns changes, the value is
discontinuous.
% Very simple environments
% break this hypothesis, such as the pendulum swing-up environment,
% with pendulum height as reward and torque as action.  Indeed, 
% % assume that $\pi$
% % is the optimal policy for the pendulum swing-up environment, with state
% % representation $(\theta, \dot{\theta})$. 
% the state space $(\theta, \dot{\theta})$ for this environment
% can be partitioned into two subspaces $\mathcal{G}$ and $\mathcal{B}$, with
% $\mathcal{G}$ the subspace where the optimal policy 
% can swing up the pendulum without crossing the $y$-axis, and $\mathcal{B}$ where
% it has to cross the $y$-axis. The difference of $V$-function between a point in
% $\mathcal{G}$ and a point in $\mathcal{B}$ is lower bounded by a finite
% quantity. 
% %Besides, one can find two points $s_1 \in \mathcal{G}$ and $s_2 \in \mathcal{B}$
% %such that $s_1$ and $s_2$ are arbitrarily close.
% Consequently, the value function is
%discontinuous on the frontier between $\mathcal{G}$ and $\mathcal{B}$, which 
This results in non infinitesimal advantages
for actions taken on the frontier. This occurs,
more generally, as soon as a given policy has different regimes depending on
where it starts in state space. For such policies the value
function is typically discontinuous at the frontier between two
regimes, resulting in non-infinitesimal advantages. The
continuous-time DAU properties would only hold almost-everywhere.}
